---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {r.oguelike}

<!-- badges: start -->

[![Project Status: WIP – Initial development is in progress, but there
has not yet been a stable, usable release suitable for the
public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)

<!-- badges: end -->

A (work-in-progress) text-based [roguelike game](https://en.wikipedia.org/wiki/Roguelike) for R.

You can install the {r.oguelike} package from GitHub:

```{r eval=FALSE}
remotes::install_github("r.oguelike")
```

To begin:

```{r eval=FALSE}
r.oguelike::start_game()
```

```
# # # # # # # # # 
# . . . . . . . # 
# . . . . . . . # 
# . . . @ . . . # 
# . $ . . . . . # 
# . . . . . . . # 
# # # # # # # # # 
Turns: 0 | Gold: 0 
Use arrow keys
```

If you're using a terminal that supports [the {keypress} package](https://github.com/gaborcsardi/keypress), then you can move the player character (`@`) with your arrow keys around the room tiles (`.`), within the walls (`#`).

So, you can press the left-arrow key and you'll move one tile to the left:

```
# # # # # # # # # 
# . . . . . . . # 
# . . . . . . . # 
# . . @ . . . . # 
# . $ . . . . . # 
# . . . . . . . # 
# # # # # # # # # 
Turns: 6 | Gold: 0
Use arrow keys
```

What happens when you touch the `$` symbol?

If playing in a {keypress}-unsupported terminal, like RStudio, then you'll be prompted to type the direction (e.g. `left`). Use `keypress::has_keypress_support()` to see if your terminal supports {keypress}.

## Code of Conduct

Please note that the {r.oguelike} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
